Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-12-25 cogsci/cogsci.Rmd
new changes

header-includes:
   - \usepackage[subtle]{savetrees}

@@

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
```

@@

How do children acquire words? An important step consists in mapping a phonological form (e.g. the sound "cat") to a semantic referent (the concept CAT). A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008). However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998). Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.

@@

A second goal of this work is to investigate how the learning mechanism develops over the life span. According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors. To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.  A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind. For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al. 2013; Pajak et al. 2016). Here we explore

Talk a bit about what we do

# Experiment 1
Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers). After training, children performed a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2). Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different. Our predictions were as follows. If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level. Finally, the pair of words that are similar on both levels should be the most difficult to learn.

@@

### Participants
We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. So far, we collected data from N=47 children (mean age= months, F=). An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as specified in the pre-registration).

### Stimuli
The sound stimuli were generated using the MBROLA Speech Synthesizer (Cite) using an American English voice. We generated two similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof"). We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
As for the objects used as semantic referents, we used the Dynamic Categories Stimuli (Cite) which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish" (plus the additional category "flower" for the catch trial). These categories are supposed to be naturally occuring kinds that might be seen on an alien planet. In each category, we generated instances that varied in their similarity by manipuating a continuous property controling features of the category's shape. This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower". All these continous properties varied on a scale from 0 to 1. We generated "similar" and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively. Examples of the resuting pairs are shown in Figure XX.

###Design 
The experiment consisted of 4 conditions which consisted, each, of a pair of sounds-objects associations. These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design. Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar to the previous ones. It involved different sounds and different objects, and it was used only to select participant who were able to follow the instructions and show minimal learning (not at chance level).

### Procedure
Children were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet. The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task. After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition. In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.

@@

The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial. The experiment can be views online using this link XX.

### Results

```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first."}

img <- png::readPNG("figs/growth2.png")
grid::grid.raster(img)

Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].  The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process. Third, it tests the generality of the findings across eight languages.

#Import data from saved
data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")

#tidy data
data_long <- data_all_scaled %>%
  gather(predictor, value, length:freq_mika)

data_long <- data_long %>%
  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))

data_long$predictor <- mapValues(data_long$predictor, 
                                 from = c("PAC_assoc", "PAC_phono_t2"), 
                                 to = c("Sem.", "Phono."))

#Compute the correlations 
correlations <-  data_long %>%
  group_by(language, predictor) %>%
  dplyr::summarise(cor = round(cor(AoA, value), 2))

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}
plot_data_all
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

#Import data from saved
degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
  dplyr::rename(Dimension = dimension)

plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
  facet_grid(. ~ language)+
  geom_point(size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme_few()+
  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
  xlab("degree") +ylab("probability")

ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)

```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph."}
plot_dist
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

# Networks
## Data
We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months). Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns. We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \ref{tab:stats} gives an overview of the data used. Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available. Note, however, that all languages have at least 60% of nouns translated.

```{r stats, results="asis", echo=FALSE}

statistics <- feather::read_feather("../saved_data/statistics.feather") 
rownames(statistics) <- NULL

tab <- xtable::xtable(statistics,
                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left). We included in our study the subset of these nouns that had available English translations (middle). The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")

print(tab, type="latex", comment = F, table.placement = "H")

#print(statistics, type="latex", comment = F, table.placement = "H")
```

## Semantic networks

We constructed semantic networks following the procedure outlined in @hills2009. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

## Phonological networks

We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

>>>>

header-includes:
   - \usepackage[subtle]{savetrees}
   - \usepackage{tipa}

@@

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(stargazer)
library(lme4)
```

@@

Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language (Werker and Tees, 1984). One could imagine that these perceptual skills would be automatically applied to the task of word learning. However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bin" and "din" to different objects (Stager & Werker, 1997).

Several factors can explain this pattern of results. For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual descrimination). In particular, it requires paying attention to both the sounds and the corresponding objects, which may hinder precise encoding in memory of some phonetic details (Stager a& Werker, 1997). Additional difficulty might arise from ambiguous phonological boundaries at this stage of development (e.g., Rost & McMurray, 2009), or from uncertainty about the referential status of the novel word (Fennell & Waxman, 2009).

Regardless of the exact explanation, it is generally accepted that by around 17 m.o, chidlren succeed under the same circumstances (Werker et al. 2002). What could be the mechanism of development? Swingley contrasted a binary-discontinuous scenario to a probabilstic-continuous one. On the discontinuous account, younger children learn a single, underspecified representation of similar words (e.g., "bin"/"din"). Development occurs when children specify this intial coarse reprepsentation and learn two distinct catgories. On the continuous account, distinct represetations are successfully learned from the start, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.

Experimental evidence suggest a probabilsitic-continuous, rather than a stage-like develomental scenario. On the one hand, 14-month-olds who typically fail in the original task succeed when learning is probed using a testing method with lower memory demands (Yoshida et al. 1009), and when uncertainty in the emerging representations is mitigated using disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016). On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases (Pajak et al., 2016; White et al., 2013).

Following this experimental studies, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task, and to explore the extent to which such a model could provide a unified accounts for several documented (as well as new) patterns of learning and development. We first present the model and explain how it can be used to make precise predictions of the target behavioral responses. Second, using new data collected from both preschool children and adults, we show how the probabilistic strucure of the model can explain behavioral patterns both within the same age and across development.

```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.  "}

img <- png::readPNG("figs/task.png")
grid::grid.raster(img)

# Model

## Task

We model a variant of the task used in Yoshida et al. 2009. In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects. After this exposure phase, participants perform a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.

<!--In previous studies, only the similarity of the sounds was varied across conditions (e.g., "bin"/"din" vs. "lif"/"neem"). In our task, we also vary the visual similarity of the objects, which allows us to explore the effect of additional probabilistic cues on novel word learning and recognition. An overview of the task is presented in Figure XX. -->

## Probabilistic strcuture

Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation. These variables are related in a way that refelects the simple generative scenario represented graphically in Figure XX. When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind. The concept prompted the cooresponding label $L$. Finally, the label was physically instantiated by the sound $s$.

```{r model, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters."}

img <- png::readPNG("figs/model.png")
grid::grid.raster(img)

Because of the noisy nature of the representations, the observer can only determine the hidden variables (i.e., the concept $C$ and the label $L$) in a probabilistic fashion. For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectivel, are normally distributed:

$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
We assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
$$
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
$$
## Predictions

During the testing phase (see Figure 1), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and two possible objects $o_1$ and $o_2$. In order to make a choice, we determine which object is more probable under the lable $s_T$, in other words, we compare the the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$. The values of these probabilities can be computed by summing over all possible labels:
$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
The joint probability $P(o, C, L, s)$ is obtained by factoring the bayesian network in Figure 2:
$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
which could be tansformed using Bayes rule into:

$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
Finally, assuming that the concept prior is a uniform ditribution, we obtain the following expression, where all conditional dependencies have been defined in the previous secton.

\begin{equation}
P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
\end{equation}

From the general expression (1) we were able to derive the exact analytical expression of the probability of correct responses in the testing phase of our simplified experimenal setting (Figure 1).

\begin{equation}
P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
\end{equation}

We simulate the values of this probability as a function of the perceptual distance between the sounds $\Delta s$, using the two remining parameters of the model: the visual distance between the semantic referents $\Delta o$ and the values of the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$). The simulations are shown in Figure 3.
```{r }

#Import data from saved
simulations <- feather::read_feather("../saved_data/simulations.feather")

plot_simulation <- ggplot(simulations, aes(x=x, y=y, col=sigma)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11),
      aspect.ratio = 0.7
      )+
  #plot.margin=grid::unit(c(0,0,0,0), "mm")
  ylim(c(0.4,1))+
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("sound distance") + ylab("Prob. accurate") +
  facet_grid(.~object_distance)

#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}
plot_simulation
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

The simulations explain previousely documented facts, and make new predictions:

1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$. This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren (Stager and Werker, 1997) and adults (Pajak et al. 2016).

2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the noise characterized with $\sigma$ decreases. This fact may explain development, i.e., youger children have noisier representations (Swingley, 2007; Yoshida et al. 2009), which lead to lower word recognition accuracy, especially for similar sounding words.

3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases when the visual distance between the semantic referents $\Delta o$ increases. This is a new predcition that our model makes. Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (see introduction), But no previous study tested the effect of the visual distance between the semantic referents.

To sum, we introduced a model that accounts for some qualitative patterns observed in previous studies, and makes new predictions. In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool chidlren and adults.

```{r}

Gdist <- function(s0, Vr, s){
  return((1/sqrt(2*pi*Vr))*exp(-(s0-s)^2/(2*Vr)))
}

s = seq(-1,2.5,0.01)
y = Gdist(0,1,s)

illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambig.') %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambig.')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambig.')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambig.')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Develop.')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Develop.')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Develop.')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Develop.'))

illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
illustration$type <- factor(illustration$type, levels = c("Disambig.", "Develop."))

probs <- subset(subset(illustration, x==0)) %>%
  group_by(type, case) %>%
  mutate(prob = round(y/sum(y),2)) %>%
  filter(rep=='1')

illus_plot <- ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=9),
      legend.text=element_text(size=9),
      axis.text = element_text(size = 9),
      strip.text = element_text(size = 9),
      axis.title = element_text(size = 9),
      aspect.ratio = 0.5
      )+

  geom_col(aes(x = x, y = y, fill = rep),
               position=position_dodge(), 
               width=0.2,
               data = subset(illustration, x==0))+
  geom_text(aes(label=paste("Acc=", prob, sep="")),
            x=1.7, y=1, size=2.5, 
            data=probs)+
  xlab("Perceptual space") + ylab("Prob") +
  facet_grid(type~case) +
  theme(legend.position="none")

```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters."}

illus_plot
```
<!--
To illustrate, imagine that $S_T = S_1$, expression XX leads to:
$$P(O_1 | S_1) \propto P(S_1|L_1)P(O_1| C_1) + P(S_1|L_2)P(O_1| C_2)$$ 
$$P(O_2 | S_1) \propto P(S_1|L_1)P(O_2| C_1) + P(S_1|L_2)P(O_2| C_2)$$

This formula explain why learners may still struggle with learning the meaning of similar words even if they learn the correct mappings. Indeed, one can learn that the sound $S_1$ is a better match to

Yet infants could have learned that bih is a better match to the ‘bih’ object than dih without triggering greater looking to the switch; the similar word could be judged to be a plausible instance of the newly learned label
-->

<!--How do children acquire words? An important step consists in mapping a phonological form (e.g. the sound "cat") to a semantic referent (the concept CAT). A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008). However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).

Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.

@@

A second goal of this work is to investigate how the learning mechanism develops over the life span. According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors. To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.  A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind. For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al. 2013; Pajak et al. 2016). Here we explore  -->

# Experiment

In this experiment, we tested participants in the word learning task introduced above (Figure 1). We explored all three parameters of the model. Both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design. Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the degree of uncertainty, $\sigma$, in the probabilsitic representations.
<!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers). After training, children performed a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2). Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different. Our predictions were as follows. If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level. Finally, the pair of words that are similar on both levels should be the most difficult to learn.  -->

@@

### Participants
We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. So far, we collected data from N=47 children (mean age= months, F=). An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as was specified in the pre-registration\footnote{https://osf.io/jrh38/}). We also collected a planed sample of N=30 adults on Amazon Mechanical Turk. N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).

### Stimuli and similarity rating
The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit et al., 1996). We generated three kinds of sound pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).

As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish". These categories are supposed to be naturally occuring kinds that might be seen on an alien planet. In each category, we generated "different", "intermediate" and "similar" levels of similarity by manipuating a continuous property controling features of the category's shape (e.g, body strech and head fatness).

In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale. We used the average ratings across participants as qunatitaive measures of sound pairs' distance ($\Delta s$) and object pairs' distance ($\Delta o$).

<!--We quantified experimetnally the similarity of sound and object pairs that we generated. 
We generated three levels of similarity pairs and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively. Examples of the resuting pairs are shown in Figure XX. 
This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower". All these continous properties varied on a scale from 0 to 1.
similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof"). We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure). -->

###Design 
Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs. "intermediate" for preschoolers, and "intermediate" vs. "similar" for adults. The experiment consisted of four conditions which involved, each, one pair of sounds-objects associations. These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group. Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participant who were able to follow the instructions and show minimal learning.

#Import data from saved
data_human_model <- feather::read_feather("../saved_data/data_human_model.feather")

data_human_model$group <- factor(data_human_model$group, levels = c("children", "adults"))

plot_data <- ggplot(data_human_model, 
#ggplot(subset(model_data_plot, group=='children'),
      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
  #geom_point()+
  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
                 position = position_dodge(width = .1),
                 size=0.2) + 
  geom_line() + 
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("Auditory similary") +ylab("Accuracy")+
  scale_colour_discrete(name="Visual similarity")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) + facet_grid(group~key, scales="free_y") +
  theme(aspect.ratio = 0.7)

#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}
plot_data
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

### Procedure

Preschoolers were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet. The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task. After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition. In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.

@@

The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial.

The procedure for preschoolers and adults were identical except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.

### Model fitting

We fit the analystical expression (equation 2) to the participants' responses in each age group.  The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (described in the stimuli sub-section). We used two models: \textbf{model 1} fit only one parameter ($\sigma = \sigma_C =\sigma_L$), and \textbf{model 2} fit two parameters ($\sigma_C  \neq \sigma_L$). The values of the parameters were derived using weighted least-squares estimates.

## Results

First we analyzed the experimental results shown in Figure (XX, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture (Barr et al. 2013). Results are shown in Table XX. We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings. We also found a main effect of object distance, thus confirming the new hypothesis derived from our model.

```{r, results='asis'}

data_child <- feather::read_feather("../saved_data/data_child.feather") %>%
  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
  rename(Accuracy = iscorrect)
data_adult <- feather::read_feather("../saved_data/data_adult.feather") %>%
  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
  rename(Accuracy = iscorrect)

model_ch <- glmer(Accuracy ~ s_dist * c_dist + 
                 (s_dist * c_dist  | ID) + 
                 (c_dist | item_object) + 
                 (s_dist | item_sound), 
               data = data_child, family = binomial(),
               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

model_ad <- glmer(Accuracy ~ s_dist * c_dist + 
                 (s_dist * c_dist  | ID) + 
                 (c_dist | sound) + 
                 (s_dist | concept), 
               data = data_adult, family = binomial(),
               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

stargazer(model_ch, model_ad, 
          column.labels = c("Children","Adults"),
          model.numbers=FALSE,
          intercept.bottom = FALSE,
          covariate.labels=c("(Intercept)","Sound ","Object","Sound x Object"),
          no.space=TRUE,
          single.row=TRUE,
          star.cutoffs =c(0.05, 0.01, 0.001),
          omit.stat = "all",
          table.layout ="-c-!t-n",
          header=FALSE,
          #notes=c("[0.*]","[0.**]"),
          title="Estimates of predictor coefficients (and their standard errors) by age group in the regression model")
```
